### 2023-10-17 ms.qmd
Updates models

pacman::p_load(tidyverse, flextable)
```

@@

# Load packages
pacman::p_load(tidyverse, flextable, brms, ggplot2,lme4, zoo)

@@

# Removing individuals who did not participate (more than 15 NAs)
data_associative <- data %>%
  group_by(lizard_id) %>%
  filter(sum(is.na(FC_associative)) <= 15) %>%
  ungroup()
data_associative <- as.data.frame(data_associative)

# Removing trials [36-40] (Only in associative)
data_associative <- data_associative %>%
group_by(lizard_id) %>%
filter(trial_associative <= 35) %>%
ungroup()
data_associative <- as.data.frame(data_associative)

@@

data_associative <- data_associative %>%
  group_by(lizard_id) %>%
  mutate(
    first_non_na = min(which(!is.na(FC_associative))),
    Associative_Trial = ifelse(!is.na(first_non_na),trial_associative - first_non_na + 1, trial_associative))%>%
    filter(Associative_Trial >= 1) %>%
   ungroup()

data_associative <- as.data.frame(data_associative)
write.csv(data_associative, file= "./output/Checking/data_associative.csv")

# Split data
deli_associative <- data_associative %>% filter (species == "delicata")
guich_associative <- data_associative %>% filter (species == "guichenoti")

@@

```{r, models}
#| label: dataclean
#| echo: false
#| warning: false

null <- glmer(FC_associative ~ 1 + (1|lizard_id), data = deli_associative, family = binomial(link = "logit"))
GMM_deli <- glmer(FC_associative ~ Associative_Trial*trt + group*Associative_Trial + (1|lizard_id), data = deli_associative, family = binomial(link = "logit"))
install.packages("lmtest")
library(lmtest)
lrtest(null, GMM_deli)
anova(GMM_deli)
plot_deli <- ggplot(deli_associative, aes(x = Associative_Trial, y = FC_associative, color=trt)) +  
geom_smooth(method = "glm", formula = y ~ x, method.args = list(family = "binomial")) +
  facet_grid(as.factor(deli_associative$group))
print(plot_deli)
```

>>>>

pacman::p_load(tidyverse, flextable, emmeans, DHARMa, brms, here, ggplot2, lme4, zoo, lmerTest)

source(here("R", "func.R"))
```

@@

@@

# Remove individuals who did not participate (more than 15 NAs), remove trials [36-40] (Only in associative) and split treatment into Temp and Cort
data_associative <- data %>%
  group_by(lizard_id) %>%
    filter(sum(is.na(FC_associative)) <= 15) %>%
    filter(trial_associative <= 35) %>%
  ungroup()  %>% 
    mutate(temp = gsub("[AB]_", "", trt),
          cort = gsub("_[2][38]", "", trt))  %>% 
    mutate(group = factor(group, levels = c("R_B", "B_R"))) %>%
  data.frame()

@@

data_associative <- data_associative %>%
  group_by(lizard_id) %>%
  mutate(
    first_non_na = min(which(!is.na(FC_associative))),
    Associative_Trial = ifelse(!is.na(first_non_na),trial_associative - first_non_na + 1, trial_associative))%>%
    filter(Associative_Trial >= 1) %>%
   ungroup() %>% data.frame()

write.csv(data_associative, file= "./output/Checking/data_associative.csv")

# Split data by species
deli_associative <- data_associative %>% filter (species == "delicata")
guich_associative <- data_associative %>% filter (species == "guichenoti")

@@

```{r, models1}
#| label: models1
#| echo: false
#| warning: false

# Generalized Mixed Models delicata
GMM_deli <- glmer(FC_associative ~ Associative_Trial*temp*cort + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = deli_associative, family = binomial(link = "logit"))
summary(GMM_deli)

emmeans(GMM_deli, pairwise ~ temp*Associative_Trial)
emmeans(GMM_deli, pairwise ~ cort*Associative_Trial)

# Generalized Mixed Models guichenoti
GMM_guich <- glmer(FC_associative ~ Associative_Trial*temp*cort + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = guich_associative, family = binomial(link = "logit"))
summary(GMM_guich)

emmeans(GMM_guich, pairwise ~ temp*Associative_Trial)
emmeans(GMM_guich, pairwise ~ cort*Associative_Trial)
emmeans(GMM_guich, pairwise ~ temp*cort*Associative_Trial)

```{r, models2}
#| label: models2
#| echo: false
#| warning: false

# Bayesian model delicata
  deli_mod <- brm(FC_associative ~ cort*temp*Associative_Trial + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = deli_associative, family = bernoulli(link = "logit"), chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
  summary(deli_mod)

# Bayesian model guichenoti
  guich_mod <- brm(FC_associative ~ cort*temp*Associative_Trial + group*Associative_Trial + (1 + Associative_Trial|lizard_id), data = guich_associative, family = bernoulli(link = "logit"), chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
  summary(deli_mod)
# R2
bayes_R2(mod)

# Extract posteriors
posterior <- posterior_samples(mod, pars = "^b")
plyr::ldply(lapply(posterior, mean))
plyr::ldply(lapply(posterior, function(x) quantile(x, c(0.025, 0.975))))
temp23 <- c(posterior[,"b_Intercept"], (posterior[,"b_Intercept"]+ posterior[,"b_trtB_23"]))
temp28 <- c((posterior[,"b_Intercept"] + posterior[,"b_trtB_28"]), posterior[,"b_trtB_23"])

pmcmc(temp23 - temp28)
dharma(GMM_deli2)

```{r, plots}
#| label: plots
#| echo: false
#| warning: false

# Plot delicata
plot_deli <- ggplot(deli_associative, aes(x = Associative_Trial, y = FC_associative, color=interaction(cort,temp))) +  
  geom_smooth(method = "glm", formula = y ~ x, method.args = list(family = "binomial"),na.action = na.exclude) +
  facet_grid(as.factor(deli_associative$group)) + 
  labs(y = "Colour Association Task", x = "Trial")  
print(plot_deli)

# Plot guichenoti
plot_guich <- ggplot(guich_associative, aes(x = Associative_Trial, y = FC_associative, color=interaction(cort,temp))) +  
  geom_smooth(method = "glm", formula = y ~ x, method.args = list(family = "binomial"),na.action = na.exclude) +
  facet_grid(as.factor(guich_associative$group)) + 
  labs(y = "Colour Association Task", x = "Trial") 
print(plot_guich)
```
